Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
8.2 Experimental Results

\textcolor{red}{There is no single tool for solving all benchmarks efficiently. In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}

>>>>

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; vZ is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, vZ returns two TOs (time-outs) in Fuzzy and Mars benchmarks.
